Automatic Extraction of JavaScript Formal Semantics from ECMAScript Specifications

### 2019-08-05 icse/related.tex
add related work

\subsection{Formal Semantics of JavaScript}
Building formal semantics of JavaScript language is 
\begin{itemize}
  \item JsVert: \cite{javert}
  \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
  \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
  \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
\end{itemize}

>>>>

\subsection{Formal Semantics of JavaScript}
Building formal semantics of language is important for program verification and static analysis. JavaScript is most widely-used language in
web browser, but its complex behavior makes confusion to developer and program analysis designer. So there are many reseraches to define formal semantics of JavaScript and
using it to formal verification or program analysis. \cite{lambdajs} define the core calculus of JavaScript, and express rest of the features as desugraing. Their method can
work for subset of JavaScript, but their formalization is not directly mapped to specification document. So it requires deep understanding of current and upcoming specification,
which needs lots of effort. \cite{kjs} and \cite{javert} defines formal semantics of JavaSciprt based on ECMAScript specification, and they manually convert from specification
to formal languages. KJS mapped from ECMAScript 5 specification to K framework, which can be used in program verifiaction and analysis. Similarly, JaVerT coverts specification
to their own language (called JSIL) to make further analysis. Compared to these approaches, we suggests to generate converter from specification to intermediate language, with
convertion assistant and layered translation technique to minimize human effort and to apply for further update or even unconfirmed proposal of specification.

% \begin{itemize}
%   \item JaVerT: JavaScript verification toolchain (POPL'18)~\cite{javert}
%   \item KJS: A complete formal semantics of JavaScript (PLDI'15)~\cite{kjs}
%   \item The Essence of JavaScript (ECOOP'10)~\cite{lambdajs}
%   \item A Trusted Mechanised JavaScript Specification (POPL'14)~\cite{jscert}
% \end{itemize}
